Human-level control through deep reinforcement learning

### 2018-01-08 article/article.tex
[Article] add plots in results + start analysis

\usepackage[utf8]{inputenc}
\usepackage[sort, colon]{natbib}
\usepackage{alifexi}
\usepackage{float}
\usepackage{subcaption}
\usepackage{color}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{commath}

\usepackage[draft,colorlinks=true,citecolor=blue,linkcolor=blue]{hyperref}
\usepackage{flushend}

@@

Schaul et al. introduced different ways to compute these ranks. We chose to prioritize with the temporal-difference error:
\begin{multline}
    \delta_t = r_t + \gamma_t Q_{target}(s_t, \argmin_a Q(s_t, a)) - Q(s_{t-1}, a_{t-1})
\end{multline}
where $Q_{target}$ is a function that applies a forward pass using the weights of the target CNN, $Q$ is a similar function
but for the first CNN, and $r_t$ is the reward received at step $t$.

To create a mini-batch, samples are selected according to a weighted distribution, where the weights are computed as follows:
\begin{multline}
    P(j) = p_i^{alpha} / \Sigma_i p_i^{alpha}
\end{multline}
$p_i$ designates the absolute value of the temporal-difference error on particular sample $i$ at current step $t$.
At the start of learning phase the vast majority of probabilities $p_i$ haven't been evaluated yet. This is why we initialized
them with a value of $1$ (which corresponds to a uniform random selection). Coefficient $\alpha$ is a hyper-parameter that
determines how strong the prioritization is. If $\alpha$ is set to zero, one falls back on the case of uniform random selection.

@@

\begin{figure*}[!t]
	\vspace{-1cm}
	\begin{subfigure}{.47\textwidth}
		\includegraphics[width=\textwidth]{figures/dqn_uniform_e_scores}
		\subcaption{Total score per episode during a learning phase of 16,000,000 steps, smoothed using a moving average with a window of size 1000.}
	\end{subfigure}
	\hfill
	\begin{subfigure}{.47\textwidth}
		\includegraphics[width=\textwidth]{figures/dqn_uniform_q_values}
		\subcaption{Estimation of $Q$, averaged across actions, for each batch during a learning phase of 16,000,000 steps and smoothed using a moving
			average with a window of size 5000.}
	\end{subfigure}
	\caption{Episode score and $Q$ values estimation of the DQN after 16,000,000 steps of training on Breakout.\label{fig:dqn uniform}}
\end{figure*}

@@

\begin{table}[!h]
	\centering
	% std of Random is 1.27 & std of DQN is 22.81
	\begin{tabular}{l|l|l|l}
		Model & Random & Human & DQN \\ \hline \hline
		Score & $1.31$ & $31.8$ & $39.88$ \\ \hline
		P &  $0\%$ & $100\%$ & $126.83\%$
	\end{tabular}
	\caption{Score and Performance on Breakout (averaged on 100 simulations with $\varepsilon=5\%$ and with one action decision per frame). The DQN has been
	trained during 16,000,000 steps.
	\todo{Ajouter scores Prioritized + DDQN et le temps d'apprentissage}\label{tab:scores breakout}}
\end{table}

@@

The implementation of t-SNE that was used is the one from Scikit-Learn~\citep{scikit-learn}, the Python library.

  \todo{Magnifique plot T-SNE avec des couleurs et des gifs et des trucs qui font beep et qui font boop. Robin est dessus. Robin gère.}~\citep{wattenberg2016how}

\begin{figure}
	\includegraphics[width=.5\textwidth]{figures/TSNE_dqn_uniform}
	\caption{\todo{Replace with correct plot}.\label{fig:t-SNE DQN uniform}}
\end{figure}

Figure~\ref{fig:dqn uniform scores dist} shows the distribution of scores when letting the DQN play for 100 games. We can see that despite having an
average score of \todo{XXX}, the DQN outputs score ranging from 7 to 219. This means that some states haven't been encountered enough for the
DQN to know significantly which one is better, and can also be slightly related to the $\epsilon$-greedy policy, yet $\epsilon$ is quite small,
and more importantly, the agent selects the action at each frame. This highest score of 219 is probably due to a non-anticipated breaking through
the brick layer, leading to the ball destroying the upper layer.

\begin{figure}
	\includegraphics[width=.5\textwidth]{figures/dqn_uniform_score_distribution}
	\caption{Distribution of the scores performed by the DQN on 100 plays.\label{fig:dqn uniform scores dist}}
\end{figure}

\begin{figure*}{!b}
	\begin{subfigure}{.47\textwidth}
		\includegraphics[width=\textwidth]{figures/dqn_uniform_e_scores}
		\subcaption{Total score per episode of the DDQN during its learning phase, smoothed using a moving average of size \todo{XXX}.}
	\end{subfigure}
	\hfill
	\begin{subfigure}{.47\textwidth}
		\includegraphics[width=\textwidth]{figures/dqn_uniform_q_values}
		\caption{Estimation of $Q$ by the DDQN, averaged across actions, for each batch during its learning phase and smoothed using a moving average
		with a window of size \todo{XXX}.}
	\end{subfigure}
	\caption{\todo{Ajouter les plots DDQN et remplacer les paths des includegraphics}.\label{fig:ddqn uniform}}
\end{figure*}

@@

\newpage
\footnotesize
\bibliographystyle{apalike}
\bibliography{article}

>>>>

\usepackage[utf8]{inputenc}
\usepackage[sort, colon]{natbib}
\usepackage{alifexi}
\usepackage{float}
\usepackage[font=small,labelfont=bf]{caption}
\usepackage{subcaption}
\usepackage{color}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{commath}

\usepackage[colorlinks=true,citecolor=blue,linkcolor=blue]{hyperref}
\usepackage{flushend}

@@

Schaul et al. introduced different ways to compute these ranks. We chose to prioritize with the temporal-difference error:
\begin{multline}
    \delta_t = r_t + \gamma_t Q_{\text{target}}\big(s_t, \argmin_a Q(s_t, a)\big) - Q(s_{t-1}, a_{t-1})
\end{multline}
where $Q_{\text{target}}$ is a function that applies a forward pass using the weights of the target CNN, $Q$ is a similar function
but for the first CNN, and $r_t$ is the reward received at step $t$.

To create a mini-batch, samples are selected according to a weighted distribution, where the weights are computed as follows:
\begin{equation}
    P(j) = p_j^{\alpha} / \sum_i p_i^{\alpha}
\end{equation}
$p_i$ designates the absolute value of the temporal-difference error on particular sample $i$ at current step $t$.
At the start of learning phase the vast majority of probabilities $p_i$ haven't been evaluated yet. This is why we initialized
them with a value of $1$ (which corresponds to a uniform random selection). Coefficient $\alpha$ is a hyper-parameter that
determines how strong the prioritization is. If $\alpha$ is set to zero, one falls back on the case of uniform random selection.

@@

\begin{figure*}[!t]
	\vspace{-1.5cm}
	\begin{subfigure}{.47\textwidth}
		\includegraphics[width=\textwidth]{figures/dqn_uniform_e_scores}
		\subcaption{Total score per episode during a learning phase of 16,000,000 steps, smoothed using a moving average with a window of size 1000.}
	\end{subfigure}
	\hfill
	\begin{subfigure}{.47\textwidth}
		\includegraphics[width=\textwidth]{figures/dqn_uniform_q_values}
		\subcaption{Estimation of $Q$, averaged across actions, for each batch during a learning phase of 16,000,000 steps and smoothed using a moving
			average with a window of size 5000.}
	\end{subfigure}
	\caption{Episode score and $Q$ values estimation of the DQN after 16,000,000 steps of training on Breakout.\label{fig:dqn uniform}}
\end{figure*}

@@

\begin{table}[!h]
	\centering
	\small
	\setlength\tabcolsep{5pt}
	\begin{tabular}{l|l|l|l|l|l}
		Model & Random & Human & DQN (U) & DQN (P) & DDQN \\ \hline \hline
		Score & $1.31$ & $31.8$ & $39.88$ & $0.22$ & $30.26$ \\ \hline
		P &  $0\%$ & $100\%$ & $126.83\%$ & $-3.57\%$ & $94.95\%$
	\end{tabular}
	\caption{Score and Performance on Breakout (averaged on 100 simulations with $\varepsilon=5\%$ and with one action decision per frame). DQN (U) represents the
	DQN with uniform replay memory, and DQN (P) represents the DQN with prioritized memory. The DQNs have been trained during 16,000,000 steps, and the DDQN has
	been trained for 7,000,000 steps.\label{tab:scores breakout}}
\end{table}

@@

The implementation of t-SNE that was used is the one from Scikit-Learn~\citep{scikit-learn}, the Python library. The parameters are the default ones:
a perplexity of 30 and a learning rate of 200 on 1000 iterations. The learning rate is quite high relatively to the propositions in~\cite{wattenberg2016how},
which allows to decrease embedding time. The perplexity lies in the range from 5 to 50 which is advised.

\todo{Parler du clustering.}

The two windows on the right of the figure show the states leading to the smallest estimated $Q$ value (blue) and the highest (red).
We can observe that the image with the smallest estimated $Q$ is an image without ball, meaning that no immediate reward is available. It
is worth noting that the DQN doesn't seem to have learned to use the FIRE action when it misses the ball. The image with the highest estimated
$Q$ is an image where the ball is about to hit a brick, leading to an immediate positive reward.

\begin{figure}[!h]
	\includegraphics[width=.5\textwidth]{figures/TSNE_dqn_uniform}
	\caption{Projection of 320,000 states onto a 2-dimensional space. The color of each dot (from dark green to yellow) represents the estimated $Q$ value of the
	best action the agent can play. The states leading to the smallest and the highest estimated $Q$ are displayed with respectively a blue and a red border.
	\label{fig:t-SNE DQN uniform}}
\end{figure}

Figure~\ref{fig:dqn uniform scores dist} shows the distribution of scores when letting the DQN play for 100 games. We can see that despite having an
average score of 39.88 (with a standard deviation of 41.14), the DQN outputs score ranging from 7 to 219. This means that some states haven't been encountered
enough for the DQN to know significantly which one is better, and can also be slightly related to the $\epsilon$-greedy policy, yet $\epsilon$ is quite small,
and more importantly, the agent selects the action at each frame. This highest score of 219 is probably due to a non-anticipated breaking through
the brick layer, leading to the ball destroying the upper layer whose bricks add 7 points to the score.

\begin{figure}[!h]
	\includegraphics[width=.5\textwidth]{figures/dqn_uniform_score_distribution}
	\caption{Distribution of the scores performed by the DQN on 100 plays.\label{fig:dqn uniform scores dist}}
\end{figure}

Figure~\ref{fig:DDQN + DQNP} shows the evolution of reward per episode and of $Q$ estimates on 16,000,000 steps for the DDQN and 7,000,000 for the DQN with
prioritized memory.

One can observe that the DDQN seems to stabilize around an average reward per episode of 1.4 (though more training time would be needed to ensure convergence),
like the DQN with uniform memory. Yet, $Q$ estimates of the DQN end up around $2$ whereas they are only half as big for the DDQN.

\begin{figure*}[!t]
	\vspace{-1.5cm}
	\begin{subfigure}{.47\textwidth}
		\includegraphics[width=\textwidth]{figures/ddqn_uniform_e_scores}
		\subcaption{Total score per episode of the DDQN using uniform memory during its learning phase, smoothed using a moving average of size 1000.}
	\end{subfigure}
	\hfill
	\begin{subfigure}{.47\textwidth}
		\includegraphics[width=\textwidth]{figures/ddqn_uniform_q_values}
		\caption{Estimation of $Q$ by the DDQN using uniform memory, averaged across actions, for each batch during its learning phase and smoothed using a moving average
		with a window of size 5000.}
	\end{subfigure}
	\begin{subfigure}{.47\textwidth}
		\vspace{-.15cm}
		\includegraphics[width=\textwidth]{figures/dqn_prioritized_e_scores}
		\subcaption{Total score per episode of the DQN with prioritized memory during its learning phase, smoothed using a moving average of size 1000.}
	\end{subfigure}
	\hfill
	\begin{subfigure}{.47\textwidth}
		\vspace{-.15cm}
		\includegraphics[width=\textwidth]{figures/dqn_prioritized_q_values}
		\caption{Estimation of $Q$ by the DQN with prioritized memory, averaged across actions, for each batch during its learning phase and smoothed using a moving average
		with a window of size 5000.}
	\end{subfigure}
	\caption{Adaptation of Figure~\ref{fig:dqn uniform} for both DDQN after 16,000,000 training steps (a and b) and DQN with prioritized memory after 7,000,000
	training steps (c and d).\label{fig:DDQN + DQNP}}
\end{figure*}

\begin{figure*}[!t]
	\vspace{-.3cm}
	\begin{subfigure}{.47\textwidth}
		\includegraphics[width=\textwidth]{figures/ddqn_uniform_score_distribution}
		\caption{Distribution of the score performed by the DDQN with uniform memory on 100 plays.}
	\end{subfigure}
	\hfill
	\begin{subfigure}{.47\textwidth}
		\includegraphics[width=\textwidth]{figures/dqn_prioritized_score_distribution}
		\caption{Distribution of the score performed by the DQN with prioritized memory on 100 plays.}
	\end{subfigure}
	\caption{Adaptation of Figure~\ref{fig:dqn uniform scores dist} for both DDQN (a) and DQN with prioritized memory (b).\label{fig:scores DDQN + DQNP}}
\end{figure*}

\todo{Continuer (ici pour ne pas flinguer la mise en page) l'analyse comparative}

@@

%\newpage
\footnotesize
\bibliographystyle{apalike}
\bibliography{article}
